---
title: "Integrating Wildfire Protection"
author: "Lilli Toone, Patricia Ma, Rachel He"
date: "11/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Integrating Wildfire Protection: Exploratory Data Analysis

### Dynamic summary

```{r echo=FALSE}
# sources all R files
source("../source/chart_1.R")
source("../source/chart_2.R")
source("../source/chart_3.R")
source("../source/summary_calc.R")
source("../source/summary_table.R")
```

### Table

**Table 1.** PMI Levels By Room

```{r echo=FALSE}
summ_table()
```

This table is ordered in descending order of the mean PMI in a typical setting, with no forest fires. Rows starting with "w" refer to rooms in the "Wurster" building, and rows starting with "f" refers to rooms in the "Fourth St." building. Rooms in the Wurster building have similar PMI's compared to rooms in the Fourth street building. The fourth street building's office had the highest average PMI for both typical and forest fire conditions. The fourth street building's empty floor had the lowest average PMI for typical conditions

### Charts
#### Chart 1: Actions to Protect

**Figure 1.** Actions that individuals take to protect against wildfire smoke.

```{r echo=FALSE}
display_chart_1()
```

This data comes from a survey in which participants ranked their own general health, then answered questions regarding their attitudes towards wildfires. This chart is important because it reveals how the general population in the greater Boise area react to protect themselves about wildfire smoke. The majority of respondents ranked themselves as either in good health or excellent health. This chart also demonstrates that staying at home was the most common course of action for those in excellent and good health. However, those in poor and fair health reported that taking medications was the most common action. Additionally, those in good health's third most popular action was to use a personal air filter. Moving to a building with an air filter was the third, and fifth choice for those in fair and good health, respectively.

#### Chart 2

#### Chart 3
